LFA analysis

### 2019-03-02 rick/LFA_Analysis.Rmd
slight changes

# Preparations

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file(), fig.width=16)
options(scipen=999)
```

@@

data <- get_data()
data <- t(as.matrix(data))
data_list <- get_af_data(data)

@@

save(data_list, '/Users/luke/Documents/QualityPaper/rick/LFA_GenotypeData.RData')

>>>>

@@

data <- get_data()
data <- t(as.matrix(data))

```{r}
data_list <- get_af_data(data)

@@

save(data_list, '/Users/luke/Documents/QualityPaper/rick/LFA_GenotypeData.RData')
```
